---
title: "07_diets_from_stable_isotopes"
author: "Peter Flood"
date: "2025-09-09"
output:
  html_document:
    toc: yes
    df_print: paged
  html_notebook:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Install and load libraries
Install if needed
```{r}
# install.packages("remotes")      # Install remotes if needed
# remotes::install_github("clquezada/tRophicPosition")
if (!require("simmr")) install.packages("simmr")
if (!require("ggrepel")) install.packages("ggrepel")
if (!require("tidyverse")) install.packages("tidyverse")
```

Load libraries
```{r}
library(simmr)
library(ggrepel)
library(tidyverse)
```

# Load and format data
Load data
```{r}
all.isotopes <- read.csv(file = "Data/Stable Isotopes/FCE1259_isotope_merge_all.csv", header = T)

herp.isotopes <- all.isotopes %>%
  filter(size_class %in% c("A.gry1", "A.mea1", "N.flo1", "N.vir1", "P.axa1", "R.gry1", "R.gry2", "S.lac1"))
```

Mean and variance per mean and species across covariate levels w/ quick visualizations
```{r}
#Plot mean per species combined for all seasons, sloughs, and habitats
all.isotope.spp.mean <- all.isotopes %>% group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) 

(all.combined.isotope.biplot <- ggplot(data = all.isotope.spp.mean, aes(x = d13C_mean, y = d15N_mean))+
    geom_text_repel(aes(label = Species))
)

srs.isotope.spp.mean <- all.isotopes %>% 
  filter(Slough =="SRS",
         Species %in% c( #filter for taxa in these models
           "SIRLAC", "AMPMEA", "NOTVIR", "NERFLO", "PSEAXA", "ACRIPT", "RANATP",
           "PERMAT", "ALGAL", "UTRPUR", "UTRFOL", "MELTUB", "PLASCA", "PSECOL", "SPHAER",
           "LUCGOO", "GAMHOL", "FUNCHR", "FUNCON", "PROFAL", "PROALL", "PROSPP", "JORFLO",
           "CYBSPP", "BELSPP", "COLEOA", "PELFEM", "CORIXI", "FLATWORM", "GERRID", "BLUE MITE", 
           "TILMAR", "HEMLET", "CICURO", "POELAT", "RANGRY", "LEPGUL", "LEPMAC", "LEPMAR", 
           "LEPMIC", "LEPPUN", "ENNGLO", "ELAEVE", "AMPHIPOD", "CHIRON", "COPEPOD", "OSTRACOD",
           "EPHEME", "BRAGRA", "CELSPP", "CORING", 
           "EPISTE", "ERYSIM", "LIBINC", "PACLON"
         )) %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) 

(srs.combined.isotope.biplot <- ggplot(data = srs.isotope.spp.mean, aes(x = d13C_mean, y = d15N_mean))+
    geom_text_repel(aes(label = Species))
)
```

Create some combined prey groups
```{r}
#dragon fly larvae - Odonata
odonates <- filter(all.isotopes, Species %in% c("BRAGRA", "CELSPP", "CORING", 
                                                "EPISTE", "ERYSIM", "LIBINC", "PACLON"),
                   Slough == "SRS") %>% 
  #group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd)) %>% 
  mutate(Species = "Odonata")

#Cyprinodontiformes - POELAT (sailfin molly) are omitted because their d13C value is quite different than the others 
cyprinodont <- all.isotopes %>% 
  filter(Species %in% c("JORFLO", "GAMHOL", "FUNCHR", "FUNCON", "LUCGOO"),
         Slough == "SRS") %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  mutate(Species = "Cyprinodont")

#Centrarchids
centrarchid <- all.isotopes %>% 
  filter(Species %in% c("LEPGUL", "LEPMAC", "LEPMAR", "LEPMIC", "LEPPUN", "ENNGLO", "ELAEVE"),
         Slough == "SRS") %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd)) %>% 
  mutate(Species = "Centrarchid")

#Crayfish
procambarus <-  all.isotopes %>% 
  filter(Species %in% c("PROALL", "PROFAL", "PROSPP"),
         Slough == "SRS") %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd)) %>% 
  mutate(Species = "Procambarus")

#Apple Snails
pomacea <- all.isotopes %>% 
  filter(Species %in% c("POMBRI", "POMPAL"),
         Slough == "SRS") %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd)) %>% 
  mutate(Species = "Pomacea")

#Aquatic snails besides apple snails
sm.snails <- all.isotopes %>% 
  filter(Species %in% c("LITMON", "MELTUB", "PLASCA", "PSECOL"),
         Slough == "SRS") %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  mutate(Species = "Small Snails")

#all snails
all.snails <- all.isotopes %>% 
  filter(Species %in% c("LITMON", "MELTUB", "PLASCA", "PSECOL", "POMBRI", "POMPAL"),
         Slough == "SRS") %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  mutate(Species = "Aquatic Snails")

#tadpoles
tadpoles <- all.isotopes %>% 
  filter(Species %in% c("ACRIPT", "RANATP"),
         Slough == "SRS") %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  mutate(Species = "Anurans")

#Green Algae - using values from Flood et al. 2023
algae <- matrix(c(3.8954, -31.8618, 0.4225, 1.1178, "Green Algae"), nrow = 1, ncol = 5)
colnames(algae) <- colnames(pomacea)
names(algae) <- names(pomacea)
algae <- algae %>% as.data.frame() %>%  mutate_at(vars(-c(Species)), as.numeric)

#SPHAER have n = 1 from TSL
#Making their own group so they get around SRS filters
sphaer <- all.isotopes %>% filter(Species == "SPHAER") %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd)) %>% 
  mutate(Species = "Sphaeriidae") 

#Coleopterans (COLEOA) only have one sample from SRS
#Pulling in TSL data here to make a group with SD
coleoa <- all.isotopes %>% filter(Species == "COLEOA") %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd)) %>% 
  mutate(Species = "Coleopterans") 

vasc.plants <- all.isotopes %>% filter(Species %in% c("CLAJAM", "ELECEL", "PONCOR")) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd)) %>% 
  mutate(Species = "Vasc. Plants") 

utricularia <- all.isotopes %>% filter(grepl("UTR", Species), Slough == "SRS") %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd)) %>% 
  mutate(Species = "Utricularia")
```

# Mixing models
## Greater Siren
Create consumer group
```{r}
sirlac <- all.isotopes %>% filter(Species == "SIRLAC") #wet and dry season 

#extract model parameters
sirlac.mix <- sirlac %>% distinct(ID, .keep_all = T) %>%  select(d13C, d15N) %>% as.matrix()
```

### Model 1
```{r}
sirlac1.prey <- all.isotopes %>% 
  filter(Species %in% c( "MELTUB", "PLASCA", "PSECOL"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(sphaer, cyprinodont, procambarus, pomacea, odonates, algae)

#SPHAER has n = 1, setting SD to the mean of the other sources for this model
sirlac1.prey[4,4] <- mean(sirlac1.prey$d15N_sd, na.rm = T) 
sirlac1.prey[4,5] <- mean(sirlac1.prey$d13C_sd, na.rm = T)

sirlac1.source.names <- as.vector(sirlac1.prey$Species)
sirlac1.source.means <- sirlac1.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
sirlac1.source.sd <- sirlac1.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
sirlac1.tef.means <- bind_cols(rep(0.3, nrow(sirlac1.prey)), rep(3.3, nrow(sirlac1.prey))) %>% 
  as.matrix()
colnames(sirlac1.tef.means) <- c("Meand13C", "Meand15N")
#sd
sirlac1.tef.sd <- bind_cols(rep(0.14, nrow(sirlac1.prey)), rep(0.26, nrow(sirlac1.prey))) %>%
  as.matrix()
colnames(sirlac1.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
sirlac1.simmr.in <- simmr_load(mixtures = sirlac.mix,
                               source_names = sirlac1.source.names,
                               source_means = sirlac1.source.means,
                               source_sds = sirlac1.source.sd,
                               correction_means = sirlac1.tef.means,
                               correction_sds = sirlac1.tef.sd)

sirlac1.simmr.in

#visualize - isospace plot
plot(sirlac1.simmr.in)


#run simmr model
sirlac1.simmr.out <- simmr_mcmc(sirlac1.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(sirlac1.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
sirlac1.simmr.out$output$`1`

summary(sirlac1.simmr.out, type = 'statistics')
summary(sirlac1.simmr.out, type = 'correlations')
summary(sirlac1.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/sirlac1_simm.csv")
# Plot the output
plot(sirlac1.simmr.out, type = 'histogram')
plot(sirlac1.simmr.out, type = 'density')
plot(sirlac1.simmr.out, type = 'matrix', size = 10)
plot(sirlac1.simmr.out, type = 'boxplot')
```

### Model 2
```{r}
sirlac2.prey <- all.isotopes %>% 
  filter(Species %in% c( "MELTUB", "PLASCA"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(sphaer, cyprinodont, procambarus, pomacea, odonates, algae)

#SPHAER has n = 1, setting SD to the mean of the other sources for this model
sirlac2.prey[3,4] <- mean(sirlac2.prey$d15N_sd, na.rm = T) 
sirlac2.prey[3,5] <- mean(sirlac2.prey$d13C_sd, na.rm = T)

sirlac2.source.names <- as.vector(sirlac2.prey$Species)
sirlac2.source.means <- sirlac2.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
sirlac2.source.sd <- sirlac2.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
sirlac2.tef.means <- bind_cols(rep(0.3, nrow(sirlac2.prey)), rep(3.3, nrow(sirlac2.prey))) %>% 
  as.matrix()
colnames(sirlac2.tef.means) <- c("Meand13C", "Meand15N")
#sd
sirlac2.tef.sd <- bind_cols(rep(0.14, nrow(sirlac2.prey)), rep(0.26, nrow(sirlac2.prey))) %>%
  as.matrix()
colnames(sirlac2.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
sirlac2.simmr.in <- simmr_load(mixtures = sirlac.mix,
                               source_names = sirlac2.source.names,
                               source_means = sirlac2.source.means,
                               source_sds = sirlac2.source.sd,
                               correction_means = sirlac2.tef.means,
                               correction_sds = sirlac2.tef.sd)

sirlac2.simmr.in

#visualize - isospace plot
plot(sirlac2.simmr.in)


#run simmr model
sirlac2.simmr.out <- simmr_mcmc(sirlac2.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(sirlac2.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
sirlac2.simmr.out$output$`1`

summary(sirlac2.simmr.out, type = 'statistics')
summary(sirlac2.simmr.out, type = 'correlations')
summary(sirlac2.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/sirlac2_simm.csv")
# Plot the output
plot(sirlac2.simmr.out, type = 'histogram')
plot(sirlac2.simmr.out, type = 'density')
plot(sirlac2.simmr.out, type = 'matrix', size = 10)
plot(sirlac2.simmr.out, type = 'boxplot')
```

### Model 3
```{r}
sirlac3.prey <- bind_rows(sphaer, cyprinodont, procambarus, pomacea, odonates, algae, sm.snails)

#SPHAER has n = 1, setting SD to the mean of the other sources for this model
sirlac3.prey[1,3] <- mean(sirlac3.prey$d15N_sd, na.rm = T) 
sirlac3.prey[1,4] <- mean(sirlac3.prey$d13C_sd, na.rm = T)

sirlac3.source.names <- as.vector(sirlac3.prey$Species)
sirlac3.source.means <- sirlac3.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
sirlac3.source.sd <- sirlac3.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
sirlac3.tef.means <- bind_cols(rep(0.3, nrow(sirlac3.prey)), rep(3.3, nrow(sirlac3.prey))) %>% 
  as.matrix()
colnames(sirlac3.tef.means) <- c("Meand13C", "Meand15N")
#sd
sirlac3.tef.sd <- bind_cols(rep(0.14, nrow(sirlac3.prey)), rep(0.26, nrow(sirlac3.prey))) %>%
  as.matrix()
colnames(sirlac3.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
sirlac3.simmr.in <- simmr_load(mixtures = sirlac.mix,
                               source_names = sirlac3.source.names,
                               source_means = sirlac3.source.means,
                               source_sds = sirlac3.source.sd,
                               correction_means = sirlac3.tef.means,
                               correction_sds = sirlac3.tef.sd)

sirlac3.simmr.in

#visualize - isospace plot
plot(sirlac3.simmr.in)


#run simmr model
sirlac3.simmr.out <- simmr_mcmc(sirlac3.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(sirlac3.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
sirlac3.simmr.out$output$`1`

summary(sirlac3.simmr.out, type = 'statistics')
summary(sirlac3.simmr.out, type = 'correlations')
summary(sirlac3.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/sirlac3_simm.csv")
# Plot the output
plot(sirlac3.simmr.out, type = 'histogram')
plot(sirlac3.simmr.out, type = 'density')
plot(sirlac3.simmr.out, type = 'matrix', size = 10)
plot(sirlac3.simmr.out, type = 'boxplot')
```

### Model 4
```{r}
sirlac4.prey <- bind_rows(sphaer, cyprinodont, procambarus, all.snails, odonates, algae)

#SPHAER has n = 1, setting SD to the mean of the other sources for this model
sirlac4.prey[1,3] <- mean(sirlac4.prey$d15N_sd, na.rm = T) 
sirlac4.prey[1,4] <- mean(sirlac4.prey$d13C_sd, na.rm = T)

sirlac4.source.names <- as.vector(sirlac4.prey$Species)
sirlac4.source.means <- sirlac4.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
sirlac4.source.sd <- sirlac4.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
sirlac4.tef.means <- bind_cols(rep(0.3, nrow(sirlac4.prey)), rep(3.3, nrow(sirlac4.prey))) %>% 
  as.matrix()
colnames(sirlac4.tef.means) <- c("Meand13C", "Meand15N")
#sd
sirlac4.tef.sd <- bind_cols(rep(0.14, nrow(sirlac4.prey)), rep(0.26, nrow(sirlac4.prey))) %>%
  as.matrix()
colnames(sirlac4.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
sirlac4.simmr.in <- simmr_load(mixtures = sirlac.mix,
                               source_names = sirlac4.source.names,
                               source_means = sirlac4.source.means,
                               source_sds = sirlac4.source.sd,
                               correction_means = sirlac4.tef.means,
                               correction_sds = sirlac4.tef.sd)

sirlac4.simmr.in

#visualize - isospace plot
plot(sirlac4.simmr.in)


#run simmr model
sirlac4.simmr.out <- simmr_mcmc(sirlac4.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(sirlac4.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
sirlac4.simmr.out$output$`1`

summary(sirlac4.simmr.out, type = 'statistics')
summary(sirlac4.simmr.out, type = 'correlations')
summary(sirlac4.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/sirlac4_simm.csv")
# Plot the output
plot(sirlac4.simmr.out, type = 'histogram')
plot(sirlac4.simmr.out, type = 'density')
plot(sirlac4.simmr.out, type = 'matrix', size = 10)
plot(sirlac4.simmr.out, type = 'boxplot')
```


### Model 5
```{r}
sirlac5.prey <- all.isotopes %>% 
  filter(Species %in% c( "POELAT"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(sphaer, cyprinodont, procambarus, all.snails, odonates, algae)

#SPHAER has n = 1, setting SD to the mean of the other sources for this model
sirlac5.prey[2,4] <- mean(sirlac5.prey$d15N_sd, na.rm = T) 
sirlac5.prey[2,5] <- mean(sirlac5.prey$d13C_sd, na.rm = T)

sirlac5.source.names <- as.vector(sirlac5.prey$Species)
sirlac5.source.means <- sirlac5.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
sirlac5.source.sd <- sirlac5.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
sirlac5.tef.means <- bind_cols(rep(0.3, nrow(sirlac5.prey)), rep(3.3, nrow(sirlac5.prey))) %>% 
  as.matrix()
colnames(sirlac5.tef.means) <- c("Meand13C", "Meand15N")
#sd
sirlac5.tef.sd <- bind_cols(rep(0.14, nrow(sirlac5.prey)), rep(0.26, nrow(sirlac5.prey))) %>%
  as.matrix()
colnames(sirlac5.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
sirlac5.simmr.in <- simmr_load(mixtures = sirlac.mix,
                               source_names = sirlac5.source.names,
                               source_means = sirlac5.source.means,
                               source_sds = sirlac5.source.sd,
                               correction_means = sirlac5.tef.means,
                               correction_sds = sirlac5.tef.sd)

sirlac5.simmr.in

#visualize - isospace plot
plot(sirlac5.simmr.in)


#run simmr model
sirlac5.simmr.out <- simmr_mcmc(sirlac5.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(sirlac5.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
sirlac5.simmr.out$output$`1`

summary(sirlac5.simmr.out, type = 'statistics')
summary(sirlac5.simmr.out, type = 'correlations')
summary(sirlac5.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/sirlac5_simm.csv")
# Plot the output
plot(sirlac5.simmr.out, type = 'histogram')
plot(sirlac5.simmr.out, type = 'density')
plot(sirlac5.simmr.out, type = 'matrix', size = 10)
plot(sirlac5.simmr.out, type = 'boxplot')
```

### Model 6
```{r}
sirlac6.prey <- all.isotopes %>% 
  filter(Species %in% c( "UTRPUR"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(sphaer, cyprinodont, procambarus, all.snails, odonates, algae)

#SPHAER has n = 1, setting SD to the mean of the other sources for this model
sirlac6.prey[2,4] <- mean(sirlac6.prey$d15N_sd, na.rm = T) 
sirlac6.prey[2,5] <- mean(sirlac6.prey$d13C_sd, na.rm = T)

sirlac6.source.names <- as.vector(sirlac6.prey$Species)
sirlac6.source.means <- sirlac6.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
sirlac6.source.sd <- sirlac6.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
sirlac6.tef.means <- bind_cols(rep(0.3, nrow(sirlac6.prey)), rep(3.3, nrow(sirlac6.prey))) %>% 
  as.matrix()
colnames(sirlac6.tef.means) <- c("Meand13C", "Meand15N")
#sd
sirlac6.tef.sd <- bind_cols(rep(0.14, nrow(sirlac6.prey)), rep(0.26, nrow(sirlac6.prey))) %>%
  as.matrix()
colnames(sirlac6.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
sirlac6.simmr.in <- simmr_load(mixtures = sirlac.mix,
                               source_names = sirlac6.source.names,
                               source_means = sirlac6.source.means,
                               source_sds = sirlac6.source.sd,
                               correction_means = sirlac6.tef.means,
                               correction_sds = sirlac6.tef.sd)

sirlac6.simmr.in

#visualize - isospace plot
plot(sirlac6.simmr.in)


#run simmr model
sirlac6.simmr.out <- simmr_mcmc(sirlac6.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(sirlac6.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
sirlac6.simmr.out$output$`1`

summary(sirlac6.simmr.out, type = 'statistics')
summary(sirlac6.simmr.out, type = 'correlations')
summary(sirlac6.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/sirlac6_simm.csv")
# Plot the output
plot(sirlac6.simmr.out, type = 'histogram')
plot(sirlac6.simmr.out, type = 'density')
plot(sirlac6.simmr.out, type = 'matrix', size = 10)
plot(sirlac6.simmr.out, type = 'boxplot')
```

### Model 7
```{r}
sirlac7.prey <- all.isotopes %>% 
  filter(Species %in% c( "UTRPUR"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(sphaer, cyprinodont, procambarus, all.snails, odonates, algae, tadpoles)

#SPHAER has n = 1, setting SD to the mean of the other sources for this model
sirlac7.prey[2,4] <- mean(sirlac7.prey$d15N_sd, na.rm = T) 
sirlac7.prey[2,5] <- mean(sirlac7.prey$d13C_sd, na.rm = T)

sirlac7.source.names <- as.vector(sirlac7.prey$Species)
sirlac7.source.means <- sirlac7.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
sirlac7.source.sd <- sirlac7.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
sirlac7.tef.means <- bind_cols(rep(0.3, nrow(sirlac7.prey)), rep(3.3, nrow(sirlac7.prey))) %>% 
  as.matrix()
colnames(sirlac7.tef.means) <- c("Meand13C", "Meand15N")
#sd
sirlac7.tef.sd <- bind_cols(rep(0.14, nrow(sirlac7.prey)), rep(0.26, nrow(sirlac7.prey))) %>%
  as.matrix()
colnames(sirlac7.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
sirlac7.simmr.in <- simmr_load(mixtures = sirlac.mix,
                               source_names = sirlac7.source.names,
                               source_means = sirlac7.source.means,
                               source_sds = sirlac7.source.sd,
                               correction_means = sirlac7.tef.means,
                               correction_sds = sirlac7.tef.sd)

sirlac7.simmr.in

#visualize - isospace plot
plot(sirlac7.simmr.in)


#run simmr model
sirlac7.simmr.out <- simmr_mcmc(sirlac7.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(sirlac7.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
sirlac7.simmr.out$output$`1`

summary(sirlac7.simmr.out, type = 'statistics')
summary(sirlac7.simmr.out, type = 'correlations')
summary(sirlac7.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/sirlac7_simm.csv")
# Plot the output
plot(sirlac7.simmr.out, type = 'histogram')
plot(sirlac7.simmr.out, type = 'density')
plot(sirlac7.simmr.out, type = 'matrix', size = 10)
plot(sirlac7.simmr.out, type = 'boxplot')
```

### Model 8
```{r}
sirlac8.prey <- all.isotopes %>% 
  filter(Species %in% c( "UTRPUR"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(sphaer, procambarus, all.snails, odonates, algae, tadpoles)

#SPHAER has n = 1, setting SD to the mean of the other sources for this model
sirlac8.prey[2,4] <- mean(sirlac8.prey$d15N_sd, na.rm = T) 
sirlac8.prey[2,5] <- mean(sirlac8.prey$d13C_sd, na.rm = T)

sirlac8.source.names <- as.vector(sirlac8.prey$Species)
sirlac8.source.means <- sirlac8.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
sirlac8.source.sd <- sirlac8.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
sirlac8.tef.means <- bind_cols(rep(0.3, nrow(sirlac8.prey)), rep(3.3, nrow(sirlac8.prey))) %>% 
  as.matrix()
colnames(sirlac8.tef.means) <- c("Meand13C", "Meand15N")
#sd
sirlac8.tef.sd <- bind_cols(rep(0.14, nrow(sirlac8.prey)), rep(0.26, nrow(sirlac8.prey))) %>%
  as.matrix()
colnames(sirlac8.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
sirlac8.simmr.in <- simmr_load(mixtures = sirlac.mix,
                               source_names = sirlac8.source.names,
                               source_means = sirlac8.source.means,
                               source_sds = sirlac8.source.sd,
                               correction_means = sirlac8.tef.means,
                               correction_sds = sirlac8.tef.sd)

sirlac8.simmr.in

#visualize - isospace plot
plot(sirlac8.simmr.in)


#run simmr model
sirlac8.simmr.out <- simmr_mcmc(sirlac8.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(sirlac8.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
sirlac8.simmr.out$output$`1`

summary(sirlac8.simmr.out, type = 'statistics')
summary(sirlac8.simmr.out, type = 'correlations')
summary(sirlac8.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/sirlac8_simm.csv")
# Plot the output
plot(sirlac8.simmr.out, type = 'histogram')
plot(sirlac8.simmr.out, type = 'density')
plot(sirlac8.simmr.out, type = 'matrix', size = 10)
plot(sirlac8.simmr.out, type = 'boxplot')
```

### Model 9
```{r}
sirlac9.prey <- all.isotopes %>% 
  filter(Species %in% c( "UTRPUR"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(procambarus, all.snails, odonates, algae, tadpoles)

sirlac9.source.names <- as.vector(sirlac9.prey$Species)
sirlac9.source.means <- sirlac9.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
sirlac9.source.sd <- sirlac9.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
sirlac9.tef.means <- bind_cols(rep(0.3, nrow(sirlac9.prey)), rep(3.3, nrow(sirlac9.prey))) %>% 
  as.matrix()
colnames(sirlac9.tef.means) <- c("Meand13C", "Meand15N")
#sd
sirlac9.tef.sd <- bind_cols(rep(0.14, nrow(sirlac9.prey)), rep(0.26, nrow(sirlac9.prey))) %>%
  as.matrix()
colnames(sirlac9.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
sirlac9.simmr.in <- simmr_load(mixtures = sirlac.mix,
                               source_names = sirlac9.source.names,
                               source_means = sirlac9.source.means,
                               source_sds = sirlac9.source.sd,
                               correction_means = sirlac9.tef.means,
                               correction_sds = sirlac9.tef.sd)

sirlac9.simmr.in

#visualize - isospace plot
plot(sirlac9.simmr.in)


#run simmr model
sirlac9.simmr.out <- simmr_mcmc(sirlac9.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(sirlac9.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
sirlac9.simmr.out$output$`1`

summary(sirlac9.simmr.out, type = 'statistics')
summary(sirlac9.simmr.out, type = 'correlations')
summary(sirlac9.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/sirlac9_simm.csv")
# Plot the output
plot(sirlac9.simmr.out, type = 'histogram')
plot(sirlac9.simmr.out, type = 'density')
plot(sirlac9.simmr.out, type = 'matrix', size = 10)
plot(sirlac9.simmr.out, type = 'boxplot')
```

## Two-Toed Amphiuma
Create consumer group
```{r}
ampmea <- all.isotopes %>% filter(Species == "AMPMEA") #dry season only

#extract model parameters
ampmea.mix <- ampmea %>% distinct(ID, .keep_all = T) %>%  select(d13C, d15N) %>% as.matrix()
```

### Model 1
```{r}
ampmea.prey <- all.isotopes %>% 
  filter(Species %in% c( "CYBSPP", "BELSPP", "PLASCA"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(coleoa, sphaer, cyprinodont, procambarus, pomacea, odonates, 
            algae, tadpoles)

#SPHAER has n = 1, setting SD to the mean of the other sources for this model
ampmea.prey[5,4] <- mean(ampmea.prey$d15N_sd, na.rm = T) 
ampmea.prey[5,5] <- mean(ampmea.prey$d13C_sd, na.rm = T)

ampmea1.source.names <- as.vector(ampmea.prey$Species)
ampmea1.source.means <- ampmea.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
ampmea1.source.sd <- ampmea.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
ampmea1.tef.means <- bind_cols(rep(0.3, nrow(ampmea.prey)), rep(3.3, nrow(ampmea.prey))) %>% 
  as.matrix()
colnames(ampmea1.tef.means) <- c("Meand13C", "Meand15N")
#sd
ampmea1.tef.sd <- bind_cols(rep(0.14, nrow(ampmea.prey)), rep(0.26, nrow(ampmea.prey))) %>%
  as.matrix()
colnames(ampmea1.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
ampmea1.simmr.in <- simmr_load(mixtures = ampmea.mix,
                               source_names = ampmea1.source.names,
                               source_means = ampmea1.source.means,
                               source_sds = ampmea1.source.sd,
                               correction_means = ampmea1.tef.means,
                               correction_sds = ampmea1.tef.sd)

ampmea1.simmr.in

#visualize - isospace plot
plot(ampmea1.simmr.in)


#run simmr model
ampmea1.simmr.out <- simmr_mcmc(ampmea1.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(ampmea1.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
ampmea1.simmr.out$output$`1`

summary(ampmea1.simmr.out, type = 'statistics')
summary(ampmea1.simmr.out, type = 'correlations')
summary(ampmea1.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/ampmea1_simm.csv")
# Plot the output
plot(ampmea1.simmr.out, type = 'histogram')
plot(ampmea1.simmr.out, type = 'density')
plot(ampmea1.simmr.out, type = 'matrix', size = 10)
plot(ampmea1.simmr.out, type = 'boxplot')
```

### Model 2
```{r}
ampmea2.prey <- all.isotopes %>% 
  filter(Species %in% c( "CYBSPP", "BELSPP", "PLASCA"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(coleoa, cyprinodont, procambarus, pomacea, odonates)

ampmea2.source.names <- as.vector(ampmea2.prey$Species)
ampmea2.source.means <- ampmea2.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
ampmea2.source.sd <- ampmea2.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
ampmea2.tef.means <- bind_cols(rep(0.3, nrow(ampmea2.prey)), rep(3.3, nrow(ampmea2.prey))) %>% 
  as.matrix()
colnames(ampmea2.tef.means) <- c("Meand13C", "Meand15N")
#sd
ampmea2.tef.sd <- bind_cols(rep(0.14, nrow(ampmea2.prey)), rep(0.26, nrow(ampmea2.prey))) %>%
  as.matrix()
colnames(ampmea2.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
ampmea2.simmr.in <- simmr_load(mixtures = ampmea.mix,
                               source_names = ampmea2.source.names,
                               source_means = ampmea2.source.means,
                               source_sds = ampmea2.source.sd,
                               correction_means = ampmea2.tef.means,
                               correction_sds = ampmea2.tef.sd)

ampmea2.simmr.in

#visualize - isospace plot
plot(ampmea2.simmr.in)


#run simmr model
ampmea2.simmr.out <- simmr_mcmc(ampmea2.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(ampmea2.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
ampmea2.simmr.out$output$`1`

summary(ampmea2.simmr.out, type = 'statistics')
summary(ampmea2.simmr.out, type = 'correlations')
summary(ampmea2.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/ampmea2_simm.csv")
# Plot the output
plot(ampmea2.simmr.out, type = 'histogram')
plot(ampmea2.simmr.out, type = 'density')
plot(ampmea2.simmr.out, type = 'matrix', size = 10)
plot(ampmea2.simmr.out, type = 'boxplot')
```

### Model 3
```{r}
ampmea3.prey <- all.isotopes %>% 
  filter(Species %in% c( "CYBSPP", "BELSPP", "PLASCA", "ALGBAL"), 
         #Algae ball (Nostoc spp.) inclusiong helps with mixing polygon
         #Howell dissertation does say "plant matter" in fecal samples
         #Pers comms said this was likely algae/diatoms
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(coleoa, cyprinodont, procambarus, pomacea, odonates)

ampmea3.source.names <- as.vector(ampmea3.prey$Species)
ampmea3.source.means <- ampmea3.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
ampmea3.source.sd <- ampmea3.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
ampmea3.tef.means <- bind_cols(rep(0.3, nrow(ampmea3.prey)), rep(3.3, nrow(ampmea3.prey))) %>% 
  as.matrix()
colnames(ampmea3.tef.means) <- c("Meand13C", "Meand15N")
#sd
ampmea3.tef.sd <- bind_cols(rep(0.14, nrow(ampmea3.prey)), rep(0.26, nrow(ampmea3.prey))) %>%
  as.matrix()
colnames(ampmea3.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
ampmea3.simmr.in <- simmr_load(mixtures = ampmea.mix,
                               source_names = ampmea3.source.names,
                               source_means = ampmea3.source.means,
                               source_sds = ampmea3.source.sd,
                               correction_means = ampmea3.tef.means,
                               correction_sds = ampmea3.tef.sd)

ampmea3.simmr.in

#visualize - isospace plot
plot(ampmea3.simmr.in)


#run simmr model
ampmea3.simmr.out <- simmr_mcmc(ampmea3.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(ampmea3.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
ampmea3.simmr.out$output$`1`

summary(ampmea3.simmr.out, type = 'statistics')
summary(ampmea3.simmr.out, type = 'correlations')
summary(ampmea3.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/ampmea3_simm.csv")
# Plot the output
plot(ampmea3.simmr.out, type = 'histogram')
plot(ampmea3.simmr.out, type = 'density')
plot(ampmea3.simmr.out, type = 'matrix', size = 10)
plot(ampmea3.simmr.out, type = 'boxplot')
```

## Peninsula Newt
Create consumer group
```{r}
notvir <- all.isotopes %>% filter(Species == "NOTVIR") #wet and dry season

#extract model parameters
notvir.mix <- notvir %>% distinct(ID, .keep_all = T) %>%  select(d13C, d15N) %>% as.matrix()
```

### Model 1
```{r}
notvir1.prey <- all.isotopes %>% 
  filter(Species %in% c( "BELSPP", "PELFEM", "CORIXI", "FLATWORM", "GERRID", "PLASCA"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(coleoa, pomacea, odonates)

#Flatworm has n = 1, setting SD to the mean of the other sources for this model
notvir1.prey[3,4] <- mean(notvir1.prey$d15N_sd, na.rm = T) 
notvir1.prey[3,5] <- mean(notvir1.prey$d13C_sd, na.rm = T)

notvir1.source.names <- as.vector(notvir1.prey$Species)
notvir1.source.means <- notvir1.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
notvir1.source.sd <- notvir1.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
notvir1.tef.means <- bind_cols(rep(0.3, nrow(notvir1.prey)), rep(3.3, nrow(notvir1.prey))) %>% 
  as.matrix()
colnames(notvir1.tef.means) <- c("Meand13C", "Meand15N")
#sd
notvir1.tef.sd <- bind_cols(rep(0.14, nrow(notvir1.prey)), rep(0.26, nrow(notvir1.prey))) %>%
  as.matrix()
colnames(notvir1.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
notvir1.simmr.in <- simmr_load(mixtures = notvir.mix,
                               source_names = notvir1.source.names,
                               source_means = notvir1.source.means,
                               source_sds = notvir1.source.sd,
                               correction_means = notvir1.tef.means,
                               correction_sds = notvir1.tef.sd)

notvir1.simmr.in

#visualize - isospace plot
plot(notvir1.simmr.in)


#run simmr model
notvir1.simmr.out <- simmr_mcmc(notvir1.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(notvir1.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
notvir1.simmr.out$output$`1`

summary(notvir1.simmr.out, type = 'statistics')
summary(notvir1.simmr.out, type = 'correlations')
summary(notvir1.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/notvir1_simm.csv")
# Plot the output
plot(notvir1.simmr.out, type = 'histogram')
plot(notvir1.simmr.out, type = 'density')
plot(notvir1.simmr.out, type = 'matrix', size = 10)
plot(notvir1.simmr.out, type = 'boxplot')
```

### Model 2
```{r}
notvir2.prey <- all.isotopes %>% 
  filter(Species %in% c( "BELSPP", "PELFEM", "FLATWORM", "GERRID", "PLASCA"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(coleoa, pomacea, odonates)

#Flatworm has n = 1, setting SD to the mean of the other sources for this model
notvir2.prey[2,4] <- mean(notvir2.prey$d15N_sd, na.rm = T) 
notvir2.prey[2,5] <- mean(notvir2.prey$d13C_sd, na.rm = T)

notvir2.source.names <- as.vector(notvir2.prey$Species)
notvir2.source.means <- notvir2.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
notvir2.source.sd <- notvir2.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
notvir2.tef.means <- bind_cols(rep(0.3, nrow(notvir2.prey)), rep(3.3, nrow(notvir2.prey))) %>% 
  as.matrix()
colnames(notvir2.tef.means) <- c("Meand13C", "Meand15N")
#sd
notvir2.tef.sd <- bind_cols(rep(0.14, nrow(notvir2.prey)), rep(0.26, nrow(notvir2.prey))) %>%
  as.matrix()
colnames(notvir2.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
notvir2.simmr.in <- simmr_load(mixtures = notvir.mix,
                               source_names = notvir2.source.names,
                               source_means = notvir2.source.means,
                               source_sds = notvir2.source.sd,
                               correction_means = notvir2.tef.means,
                               correction_sds = notvir2.tef.sd)

notvir2.simmr.in

#visualize - isospace plot
plot(notvir2.simmr.in)


#run simmr model
notvir2.simmr.out <- simmr_mcmc(notvir2.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(notvir2.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
notvir2.simmr.out$output$`1`

summary(notvir2.simmr.out, type = 'statistics')
summary(notvir2.simmr.out, type = 'correlations')
summary(notvir2.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/notvir2_simm.csv")
# Plot the output
plot(notvir2.simmr.out, type = 'histogram')
plot(notvir2.simmr.out, type = 'density')
plot(notvir2.simmr.out, type = 'matrix', size = 10)
plot(notvir2.simmr.out, type = 'boxplot')

```

### Model 3
```{r}
notvir3.prey <- all.isotopes %>% 
  filter(Species %in% c( "BELSPP", "PELFEM", "FLATWORM", "GERRID", "PLASCA"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(coleoa, pomacea, odonates, cyprinodont)

#Flatworm has n = 1, setting SD to the mean of the other sources for this model
notvir3.prey[2,4] <- mean(notvir3.prey$d15N_sd, na.rm = T) 
notvir3.prey[2,5] <- mean(notvir3.prey$d13C_sd, na.rm = T)

notvir3.source.names <- as.vector(notvir3.prey$Species)
notvir3.source.means <- notvir3.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
notvir3.source.sd <- notvir3.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
notvir3.tef.means <- bind_cols(rep(0.3, nrow(notvir3.prey)), rep(3.3, nrow(notvir3.prey))) %>% 
  as.matrix()
colnames(notvir3.tef.means) <- c("Meand13C", "Meand15N")
#sd
notvir3.tef.sd <- bind_cols(rep(0.14, nrow(notvir3.prey)), rep(0.26, nrow(notvir3.prey))) %>%
  as.matrix()
colnames(notvir3.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
notvir3.simmr.in <- simmr_load(mixtures = notvir.mix,
                               source_names = notvir3.source.names,
                               source_means = notvir3.source.means,
                               source_sds = notvir3.source.sd,
                               correction_means = notvir3.tef.means,
                               correction_sds = notvir3.tef.sd)

notvir3.simmr.in

#visualize - isospace plot
plot(notvir3.simmr.in)


#run simmr model
notvir3.simmr.out <- simmr_mcmc(notvir3.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(notvir3.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
notvir3.simmr.out$output$`1`

summary(notvir3.simmr.out, type = 'statistics')
summary(notvir3.simmr.out, type = 'correlations')
summary(notvir3.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/notvir3_simm.csv")
# Plot the output
plot(notvir3.simmr.out, type = 'histogram')
plot(notvir3.simmr.out, type = 'density')
plot(notvir3.simmr.out, type = 'matrix', size = 10)
plot(notvir3.simmr.out, type = 'boxplot')
```

### Model 4
```{r}
notvir4.prey <- all.isotopes %>% 
  filter(Species %in% c( "BELSPP", "PELFEM", "FLATWORM", "GERRID", "PLASCA", "BLUE MITE"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(coleoa, pomacea, odonates, cyprinodont)

#Flatworm has n = 1, setting SD to the mean of the other sources for this model
notvir4.prey[3,4] <- mean(notvir4.prey$d15N_sd, na.rm = T) 
notvir4.prey[3,5] <- mean(notvir4.prey$d13C_sd, na.rm = T)

notvir4.source.names <- as.vector(notvir4.prey$Species)
notvir4.source.means <- notvir4.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
notvir4.source.sd <- notvir4.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
notvir4.tef.means <- bind_cols(rep(0.3, nrow(notvir4.prey)), rep(3.3, nrow(notvir4.prey))) %>% 
  as.matrix()
colnames(notvir4.tef.means) <- c("Meand13C", "Meand15N")
#sd
notvir4.tef.sd <- bind_cols(rep(0.14, nrow(notvir4.prey)), rep(0.26, nrow(notvir4.prey))) %>%
  as.matrix()
colnames(notvir4.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
notvir4.simmr.in <- simmr_load(mixtures = notvir.mix,
                               source_names = notvir4.source.names,
                               source_means = notvir4.source.means,
                               source_sds = notvir4.source.sd,
                               correction_means = notvir4.tef.means,
                               correction_sds = notvir4.tef.sd)

notvir4.simmr.in

#visualize - isospace plot
plot(notvir4.simmr.in)


#run simmr model
notvir4.simmr.out <- simmr_mcmc(notvir4.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(notvir4.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
notvir4.simmr.out$output$`1`

summary(notvir4.simmr.out, type = 'statistics')
summary(notvir4.simmr.out, type = 'correlations')
summary(notvir4.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/notvir4_simm.csv")
# Plot the output
plot(notvir4.simmr.out, type = 'histogram')
plot(notvir4.simmr.out, type = 'density')
plot(notvir4.simmr.out, type = 'matrix', size = 10)
plot(notvir4.simmr.out, type = 'boxplot')
```

### Model 5
```{r}
notvir5.prey <- all.isotopes %>% 
  filter(Species %in% c( "BELSPP", "PELFEM", "FLATWORM", "GERRID", "PLASCA", "BLUE MITE", "AMPHIPOD"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(coleoa, pomacea, odonates, cyprinodont)

#Flatworm has n = 1, setting SD to the mean of the other sources for this model
notvir5.prey[4,4] <- mean(notvir5.prey$d15N_sd, na.rm = T) 
notvir5.prey[4,5] <- mean(notvir5.prey$d13C_sd, na.rm = T)

notvir5.source.names <- as.vector(notvir5.prey$Species)
notvir5.source.means <- notvir5.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
notvir5.source.sd <- notvir5.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
notvir5.tef.means <- bind_cols(rep(0.3, nrow(notvir5.prey)), rep(3.3, nrow(notvir5.prey))) %>% 
  as.matrix()
colnames(notvir5.tef.means) <- c("Meand13C", "Meand15N")
#sd
notvir5.tef.sd <- bind_cols(rep(0.14, nrow(notvir5.prey)), rep(0.26, nrow(notvir5.prey))) %>%
  as.matrix()
colnames(notvir5.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
notvir5.simmr.in <- simmr_load(mixtures = notvir.mix,
                               source_names = notvir5.source.names,
                               source_means = notvir5.source.means,
                               source_sds = notvir5.source.sd,
                               correction_means = notvir5.tef.means,
                               correction_sds = notvir5.tef.sd)

notvir5.simmr.in

#visualize - isospace plot
plot(notvir5.simmr.in)


#run simmr model
notvir5.simmr.out <- simmr_mcmc(notvir5.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(notvir5.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
notvir5.simmr.out$output$`1`

summary(notvir5.simmr.out, type = 'statistics')
summary(notvir5.simmr.out, type = 'correlations')
summary(notvir5.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/notvir5_simm.csv")
# Plot the output
plot(notvir5.simmr.out, type = 'histogram')
plot(notvir5.simmr.out, type = 'density')
plot(notvir5.simmr.out, type = 'matrix', size = 10)
plot(notvir5.simmr.out, type = 'boxplot')
```

## Florida Green Watersnake
Create consumer group
```{r}
nerflo <- all.isotopes %>% filter(Species == "NERFLO") #dry season only

#extract model parameters
nerflo.mix <- nerflo %>% distinct(ID, .keep_all = T) %>%  select(d13C, d15N) %>% as.matrix()
```

### Model 1
```{r}
nerflo1.prey <- all.isotopes %>% 
  filter(Species %in% c( "TILMAR", "HEMLET", "CICURO", "POELAT", "RANGRY", "CYBSPP"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(cyprinodont, centrarchid, tadpoles, procambarus, odonates)

nerflo1.source.names <- as.vector(nerflo1.prey$Species)
nerflo1.source.means <- nerflo1.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
nerflo1.source.sd <- nerflo1.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
nerflo1.tef.means <- bind_cols(rep(0.3, nrow(nerflo1.prey)), rep(3.3, nrow(nerflo1.prey))) %>% 
  as.matrix()
colnames(nerflo1.tef.means) <- c("Meand13C", "Meand15N")
#sd
nerflo1.tef.sd <- bind_cols(rep(0.14, nrow(nerflo1.prey)), rep(0.26, nrow(nerflo1.prey))) %>%
  as.matrix()
colnames(nerflo1.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
nerflo1.simmr.in <- simmr_load(mixtures = nerflo.mix,
                               source_names = nerflo1.source.names,
                               source_means = nerflo1.source.means,
                               source_sds = nerflo1.source.sd,
                               correction_means = nerflo1.tef.means,
                               correction_sds = nerflo1.tef.sd)

nerflo1.simmr.in

#visualize - isospace plot
plot(nerflo1.simmr.in)


#run simmr model
nerflo1.simmr.out <- simmr_mcmc(nerflo1.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(nerflo1.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
nerflo1.simmr.out$output$`1`

summary(nerflo1.simmr.out, type = 'statistics')
summary(nerflo1.simmr.out, type = 'correlations')
summary(nerflo1.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/nerflo1_simm.csv")
# Plot the output
plot(nerflo1.simmr.out, type = 'histogram')
plot(nerflo1.simmr.out, type = 'density')
plot(nerflo1.simmr.out, type = 'matrix', size = 10)
plot(nerflo1.simmr.out, type = 'boxplot')
```

### Model 2
```{r}
nerflo2.prey <- all.isotopes %>% 
  filter(Species %in% c( "TILMAR", "POELAT", "RANGRY", "CYBSPP"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(cyprinodont, tadpoles, procambarus, odonates)

nerflo2.source.names <- as.vector(nerflo2.prey$Species)
nerflo2.source.means <- nerflo2.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
nerflo2.source.sd <- nerflo2.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
nerflo2.tef.means <- bind_cols(rep(0.3, nrow(nerflo2.prey)), rep(3.3, nrow(nerflo2.prey))) %>% 
  as.matrix()
colnames(nerflo2.tef.means) <- c("Meand13C", "Meand15N")
#sd
nerflo2.tef.sd <- bind_cols(rep(0.14, nrow(nerflo2.prey)), rep(0.26, nrow(nerflo2.prey))) %>%
  as.matrix()
colnames(nerflo2.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
nerflo2.simmr.in <- simmr_load(mixtures = nerflo.mix,
                               source_names = nerflo2.source.names,
                               source_means = nerflo2.source.means,
                               source_sds = nerflo2.source.sd,
                               correction_means = nerflo2.tef.means,
                               correction_sds = nerflo2.tef.sd)

nerflo2.simmr.in

#visualize - isospace plot
plot(nerflo2.simmr.in)


#run simmr model
nerflo2.simmr.out <- simmr_mcmc(nerflo2.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(nerflo2.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
nerflo2.simmr.out$output$`1`

summary(nerflo2.simmr.out, type = 'statistics')
summary(nerflo2.simmr.out, type = 'correlations')
summary(nerflo2.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/nerflo2_simm.csv")
# Plot the output
plot(nerflo2.simmr.out, type = 'histogram')
plot(nerflo2.simmr.out, type = 'density')
plot(nerflo2.simmr.out, type = 'matrix', size = 10)
plot(nerflo2.simmr.out, type = 'boxplot')
```

### Model 3
```{r}
nerflo3.prey <- all.isotopes %>% 
  filter(Species %in% c( "TILMAR", "RANGRY", "CYBSPP"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(cyprinodont, tadpoles, procambarus, odonates)

nerflo3.source.names <- as.vector(nerflo3.prey$Species)
nerflo3.source.means <- nerflo3.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
nerflo3.source.sd <- nerflo3.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
nerflo3.tef.means <- bind_cols(rep(0.3, nrow(nerflo3.prey)), rep(3.3, nrow(nerflo3.prey))) %>% 
  as.matrix()
colnames(nerflo3.tef.means) <- c("Meand13C", "Meand15N")
#sd
nerflo3.tef.sd <- bind_cols(rep(0.14, nrow(nerflo3.prey)), rep(0.26, nrow(nerflo3.prey))) %>%
  as.matrix()
colnames(nerflo3.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
nerflo3.simmr.in <- simmr_load(mixtures = nerflo.mix,
                               source_names = nerflo3.source.names,
                               source_means = nerflo3.source.means,
                               source_sds = nerflo3.source.sd,
                               correction_means = nerflo3.tef.means,
                               correction_sds = nerflo3.tef.sd)

nerflo3.simmr.in

#visualize - isospace plot
plot(nerflo3.simmr.in)


#run simmr model
nerflo3.simmr.out <- simmr_mcmc(nerflo3.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(nerflo3.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
nerflo3.simmr.out$output$`1`

summary(nerflo3.simmr.out, type = 'statistics')
summary(nerflo3.simmr.out, type = 'correlations')
summary(nerflo3.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/nerflo3_simm.csv")
# Plot the output
plot(nerflo3.simmr.out, type = 'histogram')
plot(nerflo3.simmr.out, type = 'density')
plot(nerflo3.simmr.out, type = 'matrix', size = 10)
plot(nerflo3.simmr.out, type = 'boxplot')
```

### Model 4
```{r}
nerflo4.prey <- all.isotopes %>% 
  filter(Species %in% c( "RANGRY", "CYBSPP"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(cyprinodont, tadpoles, procambarus, odonates)

nerflo4.source.names <- as.vector(nerflo4.prey$Species)
nerflo4.source.means <- nerflo4.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
nerflo4.source.sd <- nerflo4.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
nerflo4.tef.means <- bind_cols(rep(0.3, nrow(nerflo4.prey)), rep(3.3, nrow(nerflo4.prey))) %>% 
  as.matrix()
colnames(nerflo4.tef.means) <- c("Meand13C", "Meand15N")
#sd
nerflo4.tef.sd <- bind_cols(rep(0.14, nrow(nerflo4.prey)), rep(0.26, nrow(nerflo4.prey))) %>%
  as.matrix()
colnames(nerflo4.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
nerflo4.simmr.in <- simmr_load(mixtures = nerflo.mix,
                               source_names = nerflo4.source.names,
                               source_means = nerflo4.source.means,
                               source_sds = nerflo4.source.sd,
                               correction_means = nerflo4.tef.means,
                               correction_sds = nerflo4.tef.sd)

nerflo4.simmr.in

#visualize - isospace plot
plot(nerflo4.simmr.in)


#run simmr model
nerflo4.simmr.out <- simmr_mcmc(nerflo4.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(nerflo4.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
nerflo4.simmr.out$output$`1`

summary(nerflo4.simmr.out, type = 'statistics')
summary(nerflo4.simmr.out, type = 'correlations')
summary(nerflo4.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/nerflo4_simm.csv")
# Plot the output
plot(nerflo4.simmr.out, type = 'histogram')
plot(nerflo4.simmr.out, type = 'density')
plot(nerflo4.simmr.out, type = 'matrix', size = 10)
plot(nerflo4.simmr.out, type = 'boxplot')
```

### Model 5
```{r}
nerflo5.prey <- all.isotopes %>% 
  filter(Species %in% c( "RANGRY"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(cyprinodont, tadpoles, procambarus, odonates)

nerflo5.source.names <- as.vector(nerflo5.prey$Species)
nerflo5.source.means <- nerflo5.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
nerflo5.source.sd <- nerflo5.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
nerflo5.tef.means <- bind_cols(rep(0.3, nrow(nerflo5.prey)), rep(3.3, nrow(nerflo5.prey))) %>% 
  as.matrix()
colnames(nerflo5.tef.means) <- c("Meand13C", "Meand15N")
#sd
nerflo5.tef.sd <- bind_cols(rep(0.14, nrow(nerflo5.prey)), rep(0.26, nrow(nerflo5.prey))) %>%
  as.matrix()
colnames(nerflo5.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
nerflo5.simmr.in <- simmr_load(mixtures = nerflo.mix,
                               source_names = nerflo5.source.names,
                               source_means = nerflo5.source.means,
                               source_sds = nerflo5.source.sd,
                               correction_means = nerflo5.tef.means,
                               correction_sds = nerflo5.tef.sd)

nerflo5.simmr.in

#visualize - isospace plot
plot(nerflo5.simmr.in)


#run simmr model
nerflo5.simmr.out <- simmr_mcmc(nerflo5.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(nerflo5.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
nerflo5.simmr.out$output$`1`

summary(nerflo5.simmr.out, type = 'statistics')
summary(nerflo5.simmr.out, type = 'correlations')
summary(nerflo5.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/nerflo5_simm.csv")
# Plot the output
plot(nerflo5.simmr.out, type = 'histogram')
plot(nerflo5.simmr.out, type = 'density')
plot(nerflo5.simmr.out, type = 'matrix', size = 10)
plot(nerflo5.simmr.out, type = 'boxplot')
```

### Model 6
```{r}
nerflo6.prey <- all.isotopes %>% 
  filter(Species %in% c("RANGRY"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(tadpoles, procambarus, cyprinodont, centrarchid)

nerflo6.source.names <- as.vector(nerflo6.prey$Species)
nerflo6.source.means <- nerflo6.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
nerflo6.source.sd <- nerflo6.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
nerflo6.tef.means <- bind_cols(rep(0.3, nrow(nerflo6.prey)), rep(3.3, nrow(nerflo6.prey))) %>% 
  as.matrix()
colnames(nerflo6.tef.means) <- c("Meand13C", "Meand15N")
#sd
nerflo6.tef.sd <- bind_cols(rep(0.14, nrow(nerflo6.prey)), rep(0.26, nrow(nerflo6.prey))) %>%
  as.matrix()
colnames(nerflo6.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
nerflo6.simmr.in <- simmr_load(mixtures = nerflo.mix,
                               source_names = nerflo6.source.names,
                               source_means = nerflo6.source.means,
                               source_sds = nerflo6.source.sd,
                               correction_means = nerflo6.tef.means,
                               correction_sds = nerflo6.tef.sd)

nerflo6.simmr.in

#visualize - isospace plot
plot(nerflo6.simmr.in)


#run simmr model
nerflo6.simmr.out <- simmr_mcmc(nerflo6.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(nerflo6.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
nerflo6.simmr.out$output$`1`

summary(nerflo6.simmr.out, type = 'statistics')
summary(nerflo6.simmr.out, type = 'correlations')
summary(nerflo6.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/nerflo6_simm.csv")
# Plot the output
plot(nerflo6.simmr.out, type = 'histogram')
plot(nerflo6.simmr.out, type = 'density')
plot(nerflo6.simmr.out, type = 'matrix', size = 10)
plot(nerflo6.simmr.out, type = 'boxplot')
```

### Model 7
```{r}
nerflo7.prey <- all.isotopes %>% 
  filter(Species %in% c("RANGRY", "TILMAR"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(tadpoles, procambarus, cyprinodont, centrarchid)

nerflo7.source.names <- as.vector(nerflo7.prey$Species)
nerflo7.source.means <- nerflo7.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
nerflo7.source.sd <- nerflo7.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
nerflo7.tef.means <- bind_cols(rep(0.3, nrow(nerflo7.prey)), rep(3.3, nrow(nerflo7.prey))) %>% 
  as.matrix()
colnames(nerflo7.tef.means) <- c("Meand13C", "Meand15N")
#sd
nerflo7.tef.sd <- bind_cols(rep(0.14, nrow(nerflo7.prey)), rep(0.26, nrow(nerflo7.prey))) %>%
  as.matrix()
colnames(nerflo7.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
nerflo7.simmr.in <- simmr_load(mixtures = nerflo.mix,
                               source_names = nerflo7.source.names,
                               source_means = nerflo7.source.means,
                               source_sds = nerflo7.source.sd,
                               correction_means = nerflo7.tef.means,
                               correction_sds = nerflo7.tef.sd)

nerflo7.simmr.in

#visualize - isospace plot
plot(nerflo7.simmr.in)


#run simmr model
nerflo7.simmr.out <- simmr_mcmc(nerflo7.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(nerflo7.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
nerflo7.simmr.out$output$`1`

summary(nerflo7.simmr.out, type = 'statistics')
summary(nerflo7.simmr.out, type = 'correlations')
summary(nerflo7.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/nerflo7_simm.csv")
# Plot the output
plot(nerflo7.simmr.out, type = 'histogram')
plot(nerflo7.simmr.out, type = 'density')
plot(nerflo7.simmr.out, type = 'matrix', size = 10)
plot(nerflo7.simmr.out, type = 'boxplot')
```

## Everglades Pygmy Siren
Create consumer group
```{r}
pseaxa <- all.isotopes %>% filter(Species == "PSEAXA") #one of each

#extract model parameters
pseaxa.mix <- pseaxa %>% distinct(ID, .keep_all = T) %>%  select(d13C, d15N) %>% as.matrix()
```

### Model 1
```{r}
pseaxa1.prey <- all.isotopes %>% 
  filter(Species %in% c("AMPHIPOD", "CHRION", "COPEPOD", "OSTRACOD", "PLASCA", "EPHEME"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(pomacea)

pseaxa1.source.names <- as.vector(pseaxa1.prey$Species)
pseaxa1.source.means <- pseaxa1.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
pseaxa1.source.sd <- pseaxa1.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
pseaxa1.tef.means <- bind_cols(rep(0.3, nrow(pseaxa1.prey)), rep(3.3, nrow(pseaxa1.prey))) %>% 
  as.matrix()
colnames(pseaxa1.tef.means) <- c("Meand13C", "Meand15N")
#sd
pseaxa1.tef.sd <- bind_cols(rep(0.14, nrow(pseaxa1.prey)), rep(0.26, nrow(pseaxa1.prey))) %>%
  as.matrix()
colnames(pseaxa1.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
pseaxa1.simmr.in <- simmr_load(mixtures = pseaxa.mix,
                               source_names = pseaxa1.source.names,
                               source_means = pseaxa1.source.means,
                               source_sds = pseaxa1.source.sd,
                               correction_means = pseaxa1.tef.means,
                               correction_sds = pseaxa1.tef.sd)

pseaxa1.simmr.in

#visualize - isospace plot
plot(pseaxa1.simmr.in)


#run simmr model
pseaxa1.simmr.out <- simmr_mcmc(pseaxa1.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(pseaxa1.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
pseaxa1.simmr.out$output$`1`

summary(pseaxa1.simmr.out, type = 'statistics')
summary(pseaxa1.simmr.out, type = 'correlations')
summary(pseaxa1.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/pseaxa1_simm.csv")
# Plot the output
plot(pseaxa1.simmr.out, type = 'histogram')
plot(pseaxa1.simmr.out, type = 'density')
plot(pseaxa1.simmr.out, type = 'matrix', size = 10)
plot(pseaxa1.simmr.out, type = 'boxplot')
```

## Cricket Frog Tadpole
Create consumer group
```{r}
acript <- all.isotopes %>% filter(Species == "ACRIPT") #2 dry, rest wet

#extract model parameters
acript.mix <- acript %>% distinct(ID, .keep_all = T) %>%  select(d13C, d15N) %>% as.matrix()
```

### Model 1
```{r}
acript1.prey <- all.isotopes %>% 
  filter(Species %in% c("PERMAT"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(algae, vasc.plants, utricularia)

acript1.source.names <- as.vector(acript1.prey$Species)
acript1.source.means <- acript1.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
acript1.source.sd <- acript1.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
acript1.tef.means <- bind_cols(rep(0.3, nrow(acript1.prey)), rep(2.2, nrow(acript1.prey))) %>% 
  as.matrix()
colnames(acript1.tef.means) <- c("Meand13C", "Meand15N")
#sd
acript1.tef.sd <- bind_cols(rep(0.14, nrow(acript1.prey)), rep(0.3, nrow(acript1.prey))) %>%
  as.matrix()
colnames(acript1.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
acript1.simmr.in <- simmr_load(mixtures = acript.mix,
                               source_names = acript1.source.names,
                               source_means = acript1.source.means,
                               source_sds = acript1.source.sd,
                               correction_means = acript1.tef.means,
                               correction_sds = acript1.tef.sd)

acript1.simmr.in

#visualize - isospace plot
plot(acript1.simmr.in)


#run simmr model
acript1.simmr.out <- simmr_mcmc(acript1.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(acript1.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
acript1.simmr.out$output$`1`

summary(acript1.simmr.out, type = 'statistics')
summary(acript1.simmr.out, type = 'correlations')
summary(acript1.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/acript1_simm.csv")
# Plot the output
plot(acript1.simmr.out, type = 'histogram')
plot(acript1.simmr.out, type = 'density')
plot(acript1.simmr.out, type = 'matrix', size = 10)
plot(acript1.simmr.out, type = 'boxplot')
```

### Model 2
```{r}
acript2.prey <-  bind_rows(algae, utricularia)

acript2.source.names <- as.vector(acript2.prey$Species)
acript2.source.means <- acript2.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
acript2.source.sd <- acript2.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
acript2.tef.means <- bind_cols(rep(0.3, nrow(acript2.prey)), rep(2.2, nrow(acript2.prey))) %>% 
  as.matrix()
colnames(acript2.tef.means) <- c("Meand13C", "Meand15N")
#sd
acript2.tef.sd <- bind_cols(rep(0.14, nrow(acript2.prey)), rep(0.3, nrow(acript2.prey))) %>%
  as.matrix()
colnames(acript2.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
acript2.simmr.in <- simmr_load(mixtures = acript.mix,
                               source_names = acript2.source.names,
                               source_means = acript2.source.means,
                               source_sds = acript2.source.sd,
                               correction_means = acript2.tef.means,
                               correction_sds = acript2.tef.sd)

acript2.simmr.in

#visualize - isospace plot
plot(acript2.simmr.in)


#run simmr model
acript2.simmr.out <- simmr_mcmc(acript2.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(acript2.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
acript2.simmr.out$output$`1`

summary(acript2.simmr.out, type = 'statistics')
summary(acript2.simmr.out, type = 'correlations')
summary(acript2.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/acript2_simm.csv")
# Plot the output
plot(acript2.simmr.out, type = 'histogram')
plot(acript2.simmr.out, type = 'density')
plot(acript2.simmr.out, type = 'matrix', size = 10)
plot(acript2.simmr.out, type = 'boxplot')
```

## Pig Frog Tadpole
Create consumer group
```{r}
ranatp <- all.isotopes %>% filter(Species == "RANATP")#2 dry, rest wet

#extract model parameters
ranatp.mix <- ranatp %>% distinct(ID, .keep_all = T) %>%  select(d13C, d15N) %>% as.matrix()
```

### Model 1
```{r}
ranatp1.prey <- all.isotopes %>% 
  filter(Species %in% c("PERMAT"),
         Slough == "SRS") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) %>% 
  bind_rows(algae, vasc.plants, utricularia)

ranatp1.source.names <- as.vector(ranatp1.prey$Species)
ranatp1.source.means <- ranatp1.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
ranatp1.source.sd <- ranatp1.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
ranatp1.tef.means <- bind_cols(rep(0.3, nrow(ranatp1.prey)), rep(3.3, nrow(ranatp1.prey))) %>% 
  as.matrix()
colnames(ranatp1.tef.means) <- c("Meand13C", "Meand15N")
#sd
ranatp1.tef.sd <- bind_cols(rep(0.14, nrow(ranatp1.prey)), rep(0.26, nrow(ranatp1.prey))) %>%
  as.matrix()
colnames(ranatp1.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
ranatp1.simmr.in <- simmr_load(mixtures = ranatp.mix,
                               source_names = ranatp1.source.names,
                               source_means = ranatp1.source.means,
                               source_sds = ranatp1.source.sd,
                               correction_means = ranatp1.tef.means,
                               correction_sds = ranatp1.tef.sd)

ranatp1.simmr.in

#visualize - isospace plot
plot(ranatp1.simmr.in)


#run simmr model
ranatp1.simmr.out <- simmr_mcmc(ranatp1.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(ranatp1.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
ranatp1.simmr.out$output$`1`

summary(ranatp1.simmr.out, type = 'statistics')
summary(ranatp1.simmr.out, type = 'correlations')
summary(ranatp1.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/ranatp1_simm.csv")
# Plot the output
plot(ranatp1.simmr.out, type = 'histogram')
plot(ranatp1.simmr.out, type = 'density')
plot(ranatp1.simmr.out, type = 'matrix', size = 10)
plot(ranatp1.simmr.out, type = 'boxplot')
```

### Model 2
```{r}
ranatp2.prey <- bind_rows(algae, utricularia)

ranatp2.source.names <- as.vector(ranatp2.prey$Species)
ranatp2.source.means <- ranatp2.prey %>% select(d13C_mean, d15N_mean) %>% as.matrix()
ranatp2.source.sd <- ranatp2.prey %>% select(d13C_sd, d15N_sd) %>% as.matrix()

#set up TEFs based on McCutchan et al 2003
#mean
ranatp2.tef.means <- bind_cols(rep(0.3, nrow(ranatp2.prey)), rep(3.3, nrow(ranatp2.prey))) %>% 
  as.matrix()
colnames(ranatp2.tef.means) <- c("Meand13C", "Meand15N")
#sd
ranatp2.tef.sd <- bind_cols(rep(0.14, nrow(ranatp2.prey)), rep(0.26, nrow(ranatp2.prey))) %>%
  as.matrix()
colnames(ranatp2.tef.sd) <- c("SDd13C", "SDd15N")

#load in simmr format
ranatp2.simmr.in <- simmr_load(mixtures = ranatp.mix,
                               source_names = ranatp2.source.names,
                               source_means = ranatp2.source.means,
                               source_sds = ranatp2.source.sd,
                               correction_means = ranatp2.tef.means,
                               correction_sds = ranatp2.tef.sd)

ranatp2.simmr.in

#visualize - isospace plot
plot(ranatp2.simmr.in)


#run simmr model
ranatp2.simmr.out <- simmr_mcmc(ranatp2.simmr.in,
                                mcmc_control = list(iter = 50000, burn = 5000, thin = 100, n.chain = 2))

#look through output
#check convergence
summary(ranatp2.simmr.out, type = "diagnostics")
# If these are close to 1 (e.g. less than 1.1) you can continue

# Now you can explore ...
ranatp2.simmr.out$output$`1`

summary(ranatp2.simmr.out, type = 'statistics')
summary(ranatp2.simmr.out, type = 'correlations')
summary(ranatp2.simmr.out, type = 'quantiles') %>% write.csv(file = "Outputs/Stable Isotopes/Diet/ranatp2_simm.csv")
# Plot the output
plot(ranatp2.simmr.out, type = 'histogram')
plot(ranatp2.simmr.out, type = 'density')
plot(ranatp2.simmr.out, type = 'matrix', size = 10)
plot(ranatp2.simmr.out, type = 'boxplot')
```

# Isotope biplot
Format data for plotting
```{r}
floc <- all.isotopes %>% 
  filter(Slough =="SRS",
         Species == "FLOC") %>% 
  group_by(Species) %>% 
  mutate_at(vars(c(d15N, d13C)), list(as.numeric)) %>% 
  summarise_at(vars(d15N, d13C), list(mean = mean, sd = sd), na.rm = T) 


all.plot.data <- bind_rows(
  srs.isotope.spp.mean %>% filter(Species != "COLEOA"),
  algae, floc, all.snails, centrarchid, 
  coleoa %>% 
    mutate(Species = gsub("Coleopterans", "COLEOA", Species)), 
  cyprinodont,
  odonates, sphaer, utricularia, vasc.plants
) %>% 
  filter(!Species %in% c("BLUE MITE")) %>% 
  mutate(`Trophic Guild` = case_when(
    Species %in% c("Vasc. Plants", "Green Algae", "PERMAT", "FLOC", "UTRFOL", "Utricularia", "UTRPUR") ~ "Basal Resources",
    Species == "Detritus" ~ "Detritus",
    Species %in% c("Collembola", "EPHEME", "Aquatic Snails", "MELTUB", "PACLON", "PLASCA",
                   "PSECOL", "Sphaeriidae") ~ "Herb. Inverts",
    Species %in% c("AMPHIPOD", "CHIRON", "COLEOA", "COPEPOD", "OSTRACOD", "CORIXI") ~ "Omni. Inverts",
    Species %in% c("BRAGRA", "BELSPP", "CELSPP", "CORING", "CYBSPP", "EPISTE", "ERYSIM",
                  "FLATWORM",  "HYDRAC", "LIBINC", "Odonata", "PELFEM") ~ "Carn. Inverts",
    Species %in% c("Palaemonetes", "PROALL", "PROFAL", "PROSPP") ~ "Decapods",
    Species %in% c("ACRIPT", "AMPMEA", "NERFLO", "NOTVIR", "PSEAXA", "RANATP", "RANGRY", "SIRLAC") ~ "Herpetofauna",
    Species %in% c("Cyprinodont", "ELAEVE", "ENNGLO", "FUNCHR", "FUNCON", "GAMHOL",
                   "JORFLO", "LUCGOO", "POELAT") ~ "Small Fishes",
    Species %in% c("Centrarchid", "CICURO", "HEMLET", "LEPGUL", "LEPMAC", "LEPMAR",
                   "LEPMIC", "LEPPUN", "TILMAR") ~ "Large Fishes"
  ),
  Order = case_when(
    `Trophic Guild` == "Basal Resources" ~ 1,
    `Trophic Guild` == "Herb. Inverts" ~ 2,
    `Trophic Guild` == "Omni. Inverts" ~ 3,
    `Trophic Guild` == "Carn. Inverts" ~ 4,
    `Trophic Guild` == "Decapods" ~ 5,
    `Trophic Guild` == "Small Fishes" ~ 6,
    `Trophic Guild` == "Large Fishes" ~ 7,
    `Trophic Guild` == "Herpetofauna" ~ 8,
  ),
  `Trophic Guild` = fct_reorder(`Trophic Guild`, Order),
  Species = case_when(
    Species == "ACRIPT" ~ "ACRITP",
    Species == "PERMAT" ~ "Periphyton",
    T ~ Species
  ),
  `Common Name` = case_when(
    Species == "ACRITP" ~ "Cricket Frog Tadpoles",
    Species == "AMPHIPOD" ~ "Scuds",
    Species == "AMPMEA" ~ "Two-Toed Amphiuma",
    Species == "BELSPP" ~ "Giant Water Bug",
    Species == "BRAGRA" ~ "Four-Spotted Pennant",
    Species == "CELSPP" ~ "Pennants",
    Species == "CHIRON" ~ "Midge Larvae",
    Species == "CICURO" ~ "Mayan Cichlid",
    Species == "COPEPOD" ~ "Copepods",
    Species == "CORING" ~ "Regal Darner",
    Species == "CORIXI" ~ "Water Boatmen",
    Species == "CYBSPP" ~ "Giant Diving Beetle",
    Species == "ELAEVE" ~ "Everglades Pygmy Sunfish",
    Species == "ENNGLO" ~ "Bluespotted Sunfish",
    Species == "EPHEME" ~ "Mayfly Larvae",
    Species == "EPISTE" ~ "Florida Baskettail",
    Species == "ERYSIM" ~ "Eastern Pondhawk",
    Species == "FLATWORM" ~ "Flatworms",
    Species == "FUNCHR" ~ "Golden Topminnow",
    Species == "FUNCON" ~ "Marsh Killifish",
    Species == "GAMHOL" ~ "Eastern Mosquitofish",
    Species == "HEMLET" ~ "African Jewelfish",
    Species == "JORFLO" ~ "Flagfish",
    Species == "LEPGUL" ~ "Warmouth",
    Species == "LEPMAC" ~ "Bluegill",
    Species == "LEPMAR" ~ "Dollar Sunfish",
    Species == "LEPMIC" ~ "Redear Sunfish",
    Species == "LEPPUN" ~ "Spotted Sunfish",
    Species == "LIBINC" ~ "Slaty Skimmer",
    Species == "LUCGOO" ~ "Bluefin Killifish",
    Species == "MELTUB" ~ "Red-Rimmed Melania",
    Species == "NERFLO" ~ "Florida Green Watersnake",
    Species == "NOTVIR" ~ "Peninsula Newt",
    Species == "OSTRACOD" ~ "Ostracods",
    Species == "PACLON" ~ "Blue Dasher",
    Species == "PELFEM" ~ "Creeping Water Bug",
    Species == "Periphyton" ~ "Periphyton",
    Species == "PLASCA" ~ "Ram's Horn Snails",
    Species == "POELAT" ~ "Sailfin Mollies",
    Species == "PROALL" ~ "Everglades Crayfish",
    Species == "PROFAL" ~ "Slough Crayfish",
    Species == "PROSPP" ~ "Juvenile Crayfish",
    Species == "PSEAXA" ~ "Everglades Dwarf Siren",
    Species == "PSECOL" ~ "American Ribbed Fluke Snail",
    Species == "RANATP" ~ "Pig Frog Tadpoles",
    Species == "RANGRY" ~ "Pig Frog",
    Species == "SIRLAC" ~ "Greater Siren",
    Species == "TILMAR" ~ "Spotted Tilapia",
    Species == "UTRFOL" ~ "Leafy Bladderwort",
    Species == "UTRPUR" ~ "Eastern Purple Bladderwort",
    Species == "Green Algae" ~ "Green Algae",
    Species == "FLOC" ~ "Benthic Flocculent Matter",
    Species == "Aquatic Snails" ~ "Aquatic Snails",
    Species == "Centrarchid" ~ "Centrarchids",
    Species == "COLEOA" ~ "Aquatic Beetles",
    Species == "Cyprinodont" ~ "Cyprinodontiforms",
    Species == "Odonata" ~ "Odonate Larvae",
    Species == "Sphaeriidae" ~ "Fingernail Clams",
    Species == "Utricularia" ~ "Bladderworts",
    Species == "Vasc. Plants" ~ "Vascular Plants"
  )
  )
```

## Plot
```{r}
(isotope.biplot.prey.groups <- ggplot(data = all.plot.data, 
                                      aes(x = d13C_mean, y = d15N_mean, color = `Trophic Guild`))+
    geom_text_repel(aes(label = `Common Name`), size = 3, max.overlaps = 20)+
    scale_color_viridis_d(end = 0.8)+
    xlab(expression(paste(delta^{13}, "C (\u2030)")))+
    ylab(expression(paste(delta^{15}, "N (\u2030)")))+
    theme_bw()+
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
  )

ggsave("Figures/Stable Isotopes/herp.iso.biplot.tiff",
       isotope.biplot.prey.groups,
       dpi = 600, width = 200, height = 150, units = "mm"
       )
```